---
title: "Happiest Country"
output: html_notebook
---
```
{r}
library(tidyverse)
library(dplyr)
library(plyr)
library(readxl)
library(data.table)
library(ggplot2)
library(hrbrthemes)
library(corrplot)
library(GGally)
library(plotly)
library(rpart)
library(rpart.plot)
library(partykit)
library(caret)
library(randomForest)
library(caTools)
library(viridis)
library(CGPfunctions)
```
```{r}
############LOADING FILES##############
data <-read.csv("Combine.csv")
data2016 <-read.csv("2016.csv")
count(data$Country)
```

```{r}
###Using data set from 2016 data set to merge with the combine data set for Region Variable:
data2016 <- data2016 %>% select(Country,Region)
combineddata <- left_join(data,data2016, by ="Country")
names(combineddata)
str(combineddata)
```
```{r}
### For some reason, the perception of corruption is character type. 
combineddata$Perceptions.of.corruption <-as.numeric(as.character(combineddata$Perceptions.of.corruption))
```
```{r}
str(combineddata)
```

```{r}
############CHECK THE FACTORS THAT MAY INCREASE THE HAPPY SCORE FROM 2017 TO 2019#######################
#2017
data2017 <-combineddata %>% filter(Year =="2017")
ggcorr(data2017[,3:9],geom ="blank", label = TRUE, hjust =1) +
  geom_point(size = 10, aes(color = coefficient > 0, alpha = abs(coefficient) > 0.5)) +
  scale_alpha_manual(values = c("TRUE" = 0.25, "FALSE" = 0)) +
  guides(color = FALSE, alpha = FALSE)+
  ggtitle("CORRELATION-2017")
```

```{r}
#2018
data2018 <-combineddata %>% filter(Year =="2018")
ggcorr(data2018[,3:9],geom ="blank", label = TRUE, hjust =1) +
  geom_point(size = 10, aes(color = coefficient > 0, alpha = abs(coefficient) > 0.5)) +
  scale_alpha_manual(values = c("TRUE" = 0.25, "FALSE" = 0)) +
  guides(color = FALSE, alpha = FALSE)+
  ggtitle("CORRELATION-2018")
```
```{r}
#2019
data2019 <-combineddata %>% filter(Year =="2019")
ggcorr(data2019[,3:9],geom ="blank", label = TRUE, hjust =1) +
  geom_point(size = 10, aes(color = coefficient > 0, alpha = abs(coefficient) > 0.5)) +
  scale_alpha_manual(values = c("TRUE" = 0.25, "FALSE" = 0)) +
  guides(color = FALSE, alpha = FALSE)+
  ggtitle("CORRELATION-2019")
```
### As we can see the major influence factors are
### GDP Per Capita, Social Support,Healthy Life Expectancy, and Freedom
### While Generosity and Corruption are not


### The graph bellows also give us a clear signal that the increase in GDP per capita will lead to the increase of Happiness Score
```{r}
combineddata$Year <-factor(combineddata$Year)
names(combineddata)
str(combineddata)
data <-combineddata
ggplot(data = data, aes(x=GDP.per.capita,y=Score, color=Year))+
  geom_point(aes(color=Year)) + 
  geom_smooth(se = FALSE)+
  labs(title ="HAPPINESS VS GDP PER CAPITA")+
  xlab("GDP PER CAPITA")+
  ylab("HAPPINESS SCORE")
```

### Also GDP per capita has strong correlation with Social Support and Healthy Life Expectancy. It would mean that citizens have more support from government and more access to medical utilities.
```{r}
ggplot(data = data, aes(x=Healthy.Life.Expectancy, y= Score, color=Year))+
  geom_point(aes(color=Year)) + 
  geom_smooth(se = FALSE)+
  scale_x_continuous(trans = 'log10')+
  labs(title ="GDP PER CAPITA VS HEALTHY")+
  xlab("GDP PER CAPITA")+
  ylab("HEALTHY")
```
```{r}
########CHECK THE VARIATION OF TOP 10 HAPPIEST COUNTRY OVER YEAR FROM 2017-2019######################
##CHANGING IN RANGE
variation1 <-combineddata %>%filter(Year!="2016" & Overall.rank <= 10) %>% mutate(Year =factor(Year),Score)
newggslopegraph(variation1,Year,Score,Country)+
  labs(title="Ranking Change over Year in Top 10",
  subtitle = "Interm of Happiness Score",
  caption = " ")
```
```{r}
##CHANGING IN GDP PER CAPITA
variation2 <-combineddata %>%filter(Year!="2016" & Overall.rank <=10)%>%mutate(Year =factor(Year),GDP.per.capita)
newggslopegraph(variation2,Year,GDP.per.capita,Country)+
  labs(title="Ranking Change over Year in Top 10",
       subtitle = "Interm of GDP Per Capita",
       caption = " ")
```
```{r}
newdf <-data2019%>%select(Country,GDP.per.capita,Region)%>%head(10)
ggplot(newdf,aes(fill=Region,x=Country,y=GDP.per.capita))+
  geom_bar(position="dodge", stat="identity")+
  theme(axis.text.x = element_text(face="bold",color="Brown",size =10, angle =90),
        axis.text.y = element_text(face = "bold",color = "Purple",size = 10))
```
#####################BUILDING MODEL TO SEE GDP PER CAPITA REALLY DETERMINES THE HAPPINESS########################
```{r}
#Check the Descriptive statistic of data
summary(data$Score)
#Create factor base on range of Score.
data$Score <-cut(data$Score,3,labels =c("(2.693,4.498)" = "Low", "(4.498,6.187]" = "Medium", "(6.187,7.769]" = "High"))
print(data$Score)
```
```{r}
###RAINFOREST:
names(data)
df2<-data%>%drop_na()%>%select(-1,-2,-10:-11) 
names(df2)
set.seed(1234)
```
```{r}
##BUILDING MODEL RAIN FOREST
sample = sample.split(df2$Score,SplitRatio = 0.75)
train<-subset(df2,sample == T)
test<-subset(df2,sample == F)
dim(train)
dim(test)
rfmodel <-randomForest(Score~.,data = train)
rfmodel
```
```{r}
predict<-predict(rfmodel,newdata = test[,-1])
table = table(test$Score,predict)
confusionMatrix(test$Score,predict)
varImp(rfmodel)
```







